NewAnalysis

### 2024-07-11 Code/NewAnalysis.Rmd
Need to change random effect event to fixed effect

```{r}
dash_and_hurdles_three_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat) + (1 | Event), 
                                   data = dash_and_hurdles,
                                   family = Gamma(link = "log"))
dash_and_hurdles_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat), 
                                   data = dash_and_hurdles,
                                   family = Gamma(link = "log"))

@@

```{r}
all_events_three_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat) + (1 | Event), 
                                   data = all_events,
                                   family = Gamma(link = "log"))
all_events_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat), 
                                   data = all_events,
                                   family = Gamma(link = "log"))
```

>>>>

```{r}
dash_and_hurdles_three_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat) + Event, 
                                   data = dash_and_hurdles,
                                   family = Gamma(link = "log"))
dash_and_hurdles_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat), 
                                   data = dash_and_hurdles,
                                   family = Gamma(link = "log"))

@@

```{r}
all_events_three_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat) + Event, 
                                   data = all_events,
                                   family = Gamma(link = "log"))
all_events_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat), 
                                   data = all_events,
                                   family = Gamma(link = "log"))
```
